Off the beaten path: \\ Gaia reveals GD-1 stars outside of the main stream

### 2018-06-21 paper/gd1.tex
proper motion selection

As a first selection of GD-1 member stars, we choose stars with proper motions
$-9 < \mu_{\phi_1, \odot} < -4.5~\masyr$ and $-1.7 < \mu_{\phi_2, \odot} <
1~\masyr$ (rectangle in the top right panel of
\figurename~\ref{fig:selection}).
\figurename~\ref{fig:selection} (top left) shows all stars that pass the
selection, plotted in the GD-1 coordinate system.
The stream is already identifiable as the overdensity of stars around $\phi_2 =
0$ between longitudes $-60^\circ \lesssim \phi_1 \lesssim 0^\circ$.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{track_observables.pdf}
\end{center}
\caption{%
Median stream properties computed from the proper motion and CMD filtered GD-1
stars, and the same for a toy model for the stream track.
\textit{Panel (a)}: Sky positions of candidate GD-1 stars.
Lines show a \changes{4th}-order polynomial fit to the median stream track offset by $\pm 0.75^\circ$; the enclosed region is adopted as the nominal stream region.
\textit{Panel (b)}: Sky positions of simulated star particles from a mock stream
model of the GD-1 stream.
\textit{Panel (c)}: Background-subtracted surface-density estimates computed in
successive, overlapping $3^\circ$ windows for both GD-1 data and the model
stream.
\textit{Panel (d)}: Median proper motion along the stream computed in the same
bins as previous panel.
\textit{Panel (e)}: Same as Panel (d), but for proper motion in stream latitude.
}
\label{fig:track-and-model}
\end{figure}

>>>>

As a first selection of GD-1 member stars, we choose stars \changes{that lie in the orange polygon in proper motions (top right panel of \figurename~\ref{fig:selection}; approximately bounded by the rectangle
$-9 < \mu_{\phi_1, \odot} < -4.5~\masyr$ and $-1.7 < \mu_{\phi_2, \odot} <
1~\masyr$).}
\figurename~\ref{fig:selection} (top left) shows all stars that pass the
selection, plotted in the GD-1 coordinate system.
The stream is already identifiable as the overdensity of stars around $\phi_2 =
0$ between longitudes $-60^\circ \lesssim \phi_1 \lesssim 0^\circ$.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{track_observables.pdf}
\end{center}
\caption{%
Median stream properties computed from the proper motion and CMD filtered GD-1
stars, and the same for a toy model for the stream track.
\textit{Panel (a)}: Sky positions of candidate GD-1 stars.
Lines show a \changes{4th}-order polynomial fit to the median stream track offset by $\pm 0.75^\circ$; the enclosed region is adopted as the nominal stream region.
\textit{Panel (b)}: Sky positions of simulated star particles from a mock stream
model of the GD-1 stream.
\textit{Panel (c)}: Background-subtracted surface-density estimates computed in
successive, overlapping $3^\circ$ windows for both GD-1 data and the model
stream.
\textit{Panel (d)}: Median proper motion along the stream computed in the same
bins as previous panel \changes{(not solar reflex corrected)}.
\textit{Panel (e)}: Same as Panel (d), but for proper motion in stream latitude.
}
\label{fig:track-and-model}
\end{figure}
